Explainable Functional Region Identification

### 2018-11-25 paper.tex
补文字部分

\documentclass[runningheads]{llncs}
\usepackage{bm}
\usepackage{CJK}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{tikz}
\usetikzlibrary{fit,positioning}

@@

%figure ??? real example or made-up example
As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions. For a specific region $r$ with label $l$, the system delivers textual and visual descriptions. Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from mobility data, coefficients of activity ``'' and ``'' to the traffic flow of region $r$ are $0.6$ and $0.4$ respectively. Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews. Finally region $r$'s most representative urban features are exactly ``" and ``", thus the system explains why $r$ is labeled as $l$.

@@

\begin{figure}
\centering
\caption{An illustrative example of Explainable Functional Region Identification (EFRI)}
\label{explanation-example} %% label for entire figure
\end{figure}

@@

\subsection{Urban Activity Extraction}
%technical details for extracting textual phrases 
To obtain a high-quality seed list of phrases , we start with a taxonomy of urban activities. Describe the taxonomy here, number of activities, why it is good to start with, etc.

%is it too many or too few? If it's too many, use the seed list as a supervision set. If it's too few, describe the filtering method below.
However, the seed list is too ...
Intuitively, a good activity phrase should...
Therefore, ...

%group textual data based on activity
We obtain a set of activity phrases $\mathcal{A}=\{a\}$ after the above two steps.
We group the textual data based on the recognized activity phrases. 
Technical details here...specify what you do when there are several activities in a sentence/review.

\subsection{Urban Feature Extraction}
%features
Previous studies on opinion mining for product recommendations~\cite{} have achieved remarkable success in extracting product aspects, i.e. with a precision as high as $\%$.
Inspired by~\cite{}, we also use a rule-based approach to extract a candidate list for urban features.
As we are building a candidate list, the primal objective is to obtain high coverage instead of high precision. 
We modify the rules to (if necessary, add a table of rules here)...
Technical details here...

%filter features
\emph{Urban features} distinguish with product aspect in that ...
Intuitively, a phrase indicating an urban feature must...
As forth, we use statistics such as ...

Equation here

As shown in Table~\ref{tab:urbanfeatures}

@@

\subsection{Urban Sentiment Extraction}
%sentiment 
We do not focus on word-level sentiment analysis in this paper.
The state-of-the-art toolkit is used...
technical details here

%aggregate sentiments
However, the problem of aggregating word-level sentiments to activity must be addressed.
intuition here...
technical details here...
result is $U_a$, describe

@@

\subsection{Model Inference}
Finally, we set up the objective function for layered regression model.
\begin{eqnarray}
\min \mathcal{L} & =\sum_{f_{r,l,t}\in F}(f_{r,l,t}-\hat{r}_{r,l,t})^2+\lambda_1 (\sum_t b_t^2  + \sum_r \|\mathbf{V}_r\|^2 )\\\nonumber
& +\lambda_2(\sum_l \|\mathbf{c}_l\|_1)+\lambda_3(\sum_i y_i^2)\\\nonumber
& w.r.t. \forall l, \mathbf{c}_l\geq \mathbf{0}
\label{equ:loss}
\end{eqnarray}

@@

\begin{eqnarray}
inference equation here
\label{equ:sgd}
\end{eqnarray}

@@

\subsection{Experimental Setup}
The data sets for our experiments include a mobility data set and a textual data set.
The mobility data (Didi dataset) is a set of  pick-up and drop-off coordinates of taxicabs with timestamps.
Statistics: e.g. number of pickup-dropoffs , time period, in which city....
The textual data set (Dianping dataset) is a set of ...
It is crawled from China's largest online review sits\footnote{www.dianping.com.cn} in ....
The data set contains xxx POIs, xxx comments

@@

%preprocessing
To obtain the input for EFRI, we implement four pre-processing steps: (1) region segmentation; (2) FRI on mobility data; (3) data set linking; (4) text cleaning.

\textbf{Region segmentation.} To form the basic city regions, we segment the urban area by the city's major road network.
The longitude of the map range in Didi dataset is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.% do we have to provide the range? in other words, how do you get the range?  
We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid by the Raster-based model~\cite{}.
The road network is converted to a grey image, where in each grid 1 stands for the road and $0$ otherwise. %?????
 The dilation and thinning process~\cite{} is operated to remove small regions such as lanes and road overpasses and simplify the map.

\textbf{FRI on mobility data.} We use DMR~\cite{} to identify region functionals and label them with  8/4 types. % what do you mean by 8/4?
Any parameters in DMR?
Note that we can use any convenient FRI system to identify region functionals.
The DMR results are illustrated in Figure~\ref{fig:DMR}

@@

\textbf{Data set linking.} we ??how do you link the two datasets?
remove any POIs?

\textbf{Text Cleaning.} Chinese word segmentation? stopword removal?
activity extraction?
Statistics of the combined dataset are shown in Table~\ref{tab:dataset}.
Averagely, a POI is associated with xxx comments....more statistics

\begin{table}[h]
\caption{Statistics of dataset}\label{tab:dataset}
\begin{tabular}{|c|c|c|c|c|}
\hline
\#POIs & \#Comments & \#Mobility pairs & \#Regions & \#Labels \\
\end{tabular}
\end{table}

\subsection{Urban Feature Extraction}

\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) (2) (3) (4) (5)

\textbf{Evaluation metrics.} (1) (2) (3) (4)equations here

\begin{table}[h]
\caption{Comparative performance of urban feature extraction}\label{tab:extraction}
\begin{tabular}{|c|c|c|c|c|}
\hline
Method & Metric 1 & Metric 2 & Metric 3 & Metric 4\\\hline
\end{tabular}
\end{table}

As shown in Table~\ref{tab:extraction}, your analysis here.

@@

\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) (2) (3)

\textbf{Evaluation metrics.} Evaluation of explainable systems is still an open problem. In this work, we consider two categories of evaluation metrics. The first is objective to evaluate the quantity of explanations. (1) EP: percentage of regions that could find explanation label by our framework. The rest are subjective to evaluate the quality of explanations.  (2) (3) (4) All reported results are averaged over regions.

equations here 
$$explanation\ percentage=\frac{|regions\ with\ explanation\ label|}{|all\ regions|}$$

\textbf{Evaluation Process}  how many human judges? how to vote?

\begin{table}[h]
\caption{Comparative performance of explainability }\label{tab:explainablity}
\begin{tabular}{|c|c|c|c|c|}
\hline
Method & Metric 1 & Metric 2 & Metric 3 & Metric 4\\\hline
\end{tabular}
\end{table}

As shown in Table~\ref{tab:explainability}, your analysis here.

@@

\bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
    Zhang Y, Lai G, Zhang M, et al. Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval. ACM, 2014:83-92.

\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017
\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63-72.
    %explain AI
\bibitem{Korpan2017navigation}Korpan, R., Epstein, S.L., Aroor, A., Dekel, G.: WHY: Natural explanations from a robot navigator. In: AAAI 2017 Fall Symposium on Natural Communication for Human-Robot Collaboration.
\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems. In Proceedings of the First International Workshop on Comprehensibility and Explanation in AI \& ML, 2017.
\bibitem{Lu2011Label}Lu Y, Castellanos M, Dayal U, et al. Automatic construction of a context-aware sentiment lexicon:an optimization approach[C]// International Conference on World Wide Web, WWW 2011, Hyderabad, India, March 28 - April. DBLP, 2011:347-356.
\bibitem{Zhang2017Model}Zhang X , Zhao J , Lui J C S . Modeling the Assimilation-Contrast Effects in Online Product Rating Systems: Debiasing and Recommendations[C]// Eleventh Acm Conference on Recommender Systems. ACM, 2017.
\bibitem{Mimno2012DMR}Mimno D, Mccallum A. Topic Models Conditioned on Arbitrary Features with Dirichlet-multinomial Regression[J]. University of Massachusetts - Amherst, 2012, 2008:411--418.
\end{thebibliography}
\end{document}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{amsmath,amssymb,amstext}
\usepackage{bm}
\usepackage{CJK}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{tikz}
\usetikzlibrary{fit,positioning}

@@

%figure ??? real example or made-up example
As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions. For a specific region $r$ with label $l$, the system delivers textual and visual descriptions. Firstly label $l$ is most likely to relate to a mixture of activities ``Business'' and ``School'', because from mobility data, coefficients of activity ``Business'' and ``School'' to the traffic flow of region $r$ are $0.7$ and $0.3$ respectively. Secondly, under activity ``Business", two urban features ``Service'' and ``Taste" are most popular, with highly positive sentiments collected from online reviews. Finally region $r$'s most representative urban features are exactly ``Service" and ``Taste", thus the system explains why $r$ is labeled as $l$.

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{overview.png}
\caption{An illustrative example of Explainable Functional Region Identification (EFRI)}
\label{explanation-example} %% label for entire figure
\end{figure}

@@

\subsection{Urban Activity Extraction}\label{sec:urbanactivityextraction}
%technical details for extracting textual phrases
To obtain a high-quality seed list of phrases , we start with a taxonomy of urban activities.
The taxonomy comes from the self-tags that taken by commented items.
They are given 16 different types of tags, and most of them are consumption.
They form 16 activity sample in the taxonomy, including Residence, Clothing, Study and Scenery and so on.
The taxonomy is easy to obtain and can be used for more activities.

%is it too many or too few? If it's too many, use the seed list as a supervision set. If it's too few, describe the filtering method below.
However, the seed list is too few to describe various functions.
Intuitively, a good activity phrase should have the ability to find the major function of at least a label.
The quantity of few activity constrains the activities hidden in textual data.
Therefore, we applied a k-Nearest Neighbor(KNN) to find more activity phrases based on the 16 activity samples mentioned in last step.
We select all words whose property is noun and sort them into vectors with word embedding.
By measure the consine distance between two vectors that stands for two words, we can find the k closest neighbors of each word.
Different with traditional kNN, we aim to find suitable activity features instead of classification.
A word can be select as activity if the score of positive examples, i.e. selected activity phrases, in its k neighbor are larger than a threshold.
There is very few positive examples in the beginning, so we give the 16 original activity a large weight.
Meanwhile, the confidence of later positive examples is set by their neighbors.
A word with many positive example neighbors and high-weight neighbors would get high weight.
The process consists until no new activity is found.

%group textual data based on activity
We obtain a set of activity phrases $\mathcal{A}=\{a\}$ after the above two steps.
We group the textual data based on the recognized activity phrases.
A sentence include a activity means it is contains relative information about the activity. 
We can classify it into the responding activity.
Specially, a sentence may include several activities, which could be analysed in different activities without conflict.

\subsection{Urban Feature Extraction}\label{sec:urbanfeatureextraction}
%features
Previous studies on opinion mining for product recommendations~\cite{Zhang2014ExplicitFactor} have achieved remarkable success in extracting product aspects, i.e. with a precision more than $90\%$.
In our EFRI models, the features would be displayed as explanation for the labels, which relate the activities with labels.
A high similarity between activities and urban features would help improve the persuasiveness of our explanation.
In next step, we will find sentiment correlate with urban features in grouped textual data of activity.
Similarity between activity and features also provide more analytical corpus.
Therefore, we choose word2vec~\cite{Mikolov2013Word2vec} to find the most relative words between selected activities.
Word2vec is superior than consine distance in terms of similarity of semantics, for it is based on complex neural network.
A feature semantically similar to activity make user easier to associate the feature with possible activities.
Feature is a word with a similarity accumulation with each activity phrase large than a threshold.
Frequency from statistic is also an important criteria here.
As we are building a candidate list, the primal objective is to obtain high coverage instead of high precision.

%filter features
\emph{Urban features} distinguish with product aspect in that it denotes geographical characters of different functional region.
Intuitively, a phrase indicating an urban feature must be relative to special characters as well as make distinguishment in regions with different labels
As forth, we use information gain(IG) to selected our urban features as:

\begin{align*}
IG(word) =& H(C)-H(C|W)\\
=&-\sum_{i=1}^{k}P(C_i)\log_2P(C_i)+P(word)\sum_{i=1}^{k}P(C_i|word)\log_2P(C_i|word)\\
&+P(\overline{word})\sum_{i=1}^{k}P(C_i|\overline{word})\log_2P(C_i|\overline{word})
\end{align*}
where $P(word)$ is the proportion the word while $P(\overline{word}) = 1- P(word)$;
$C_i$ denotes the $i$-th class;
information entropy $H(C)$ reflects the degree of uncertainty of information. The greater the entropy, the more unstable the features are;
conditional entropy $H(C|W)$ demonstrates the degree of uncertainty after classification according to this feature, and a small conditional entropy denotes a more stable case after classification.
A high IG value means the word contributes a lot in such a classification.
and we select features with highest IG value as urban features.

The selected features are shown in Table~\ref{tab:urbanfeatures}

@@

\subsection{Urban Sentiment Extraction}
%sentiment
We do not focus on word-level sentiment analysis in this paper.
The common used approach to get sentiment score is based on lexicon.
We rate the sentiment score of textual data with a existed lexicon with.
Each word in the lexicon has a trained rate of sentiment.
With the sopport of stopwords, negative words and adverbs with degree, we could get the sentiment rating of whole sentence.

%aggregate sentiments
However, the problem of aggregating word-level sentiments to activity must be addressed.
In the Section~\ref{sec:urbanactivityextraction}, we have group textual data with different activities.
And in the Section~\ref{sec:urbanfeatureextraction}, we extract urban feature by similarity with activities.
Due to the similarity we could find enough relevant textual data between each pair of activities and urban features.
For each activity $a$, we search each urban feature in its corresponding textual data.
If a sentence in textual data of $a$ contains urban feature $k$, we calculate its sentiment score as a candidate value of $U_{a,k}$.
The final value of $U_{a,c}$ is the average value of its candidates.
To fit the sentiment polarity, we map each value of $U_{a,c}$ into the range of $[-1,1]$ by a variant of $sigmoid$ function as:
$$f(x) =\frac{2}{1+\exp(-x)}-1$$
Now we get a matrix $U$, which denotes the sentiment on corresponding activities and urban features.

@@

\subsection{Model Inference}
Finally, we set up the objective function for layered regression model.
\begin{eqnarray}
\min \mathcal{L} & =\sum_{f_{r,l,t}\in F}(f_{r,l,t}-\hat{f}_{r,l,t})^2+\lambda_1 (\sum_t b_t^2  + \sum_r \|\mathbf{V}_r\|^2 )\\\nonumber
& +\lambda_2(\sum_l \|\mathbf{c}_l\|_1)+\lambda_3(\sum_i y_i^2)\\\nonumber
& w.r.t. \forall l, \mathbf{c}_l\geq \mathbf{0}
\label{equ:loss}
\end{eqnarray}

@@

\begin{align*}
b_t &= b_t - \gamma\left(-2\times\left(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\right)+2\times\lambda_1\times b_t\right)\\
V_{f,r} &= V_{f,r} - \gamma\left(-2\times\left(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\times\left(\sum_ac_{l,a}\times U_{a,f}\right)\right)+2\times\lambda_1\times V_{f,r}\right)\\
c_{l,a} &= c_{l,a} - \gamma\left(-2\times(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\times(U_a^TV_r + \beta_{a,t}(\hat{f}_{r,l,t-1})))+\lambda_2\right)\\
y_i &= y_i - \gamma\left(-2\times\left(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\times\left(\sum_a c_{l,a}\frac{k_h(\hat{f}_{r,l,t-1}-x_j)}{\sum_{j=1}^n k_h(\hat{f}_{r,l,t-1}-x_j)   }\right)\right)+2\times\lambda_3\times y_i\right)\\
\label{equ:sgd}
\end{align*}

@@

\subsection{Experimental Setup}
The data sets for our experiments include a mobility data set and a textual data set.
The mobility data (Didi dataset) is a set of  pick-up and drop-off coordinates of taxicabs with timestamps.
It contains more than 7 million pick-up and drop-off pairs in November 2016.
The textual data set (Dianping dataset) is a set of comments of various items. 
It is crawled from China's largest online review sites\footnote{www.dianping.com.cn} in .... % in what...
The data set contains 109686 POIs and 3213264 comments.

@@

%preprocessing
To obtain the input for EFRI, we implement four pre-processing steps: (1) region segmentation; (2) data set linking; (3)FRI on mobility data; (4) text cleaning.

\textbf{Region segmentation.} To form the basic city regions, we segment the urban area by the city's major road network.
The longitude of the map range in Didi dataset is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.% do we have to provide the range? in other words, how do you get the range?
We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid by ArcMap, a professional map processing software.
The road network is converted to a grey image, where in each grid 1 stands for the road and $0$ otherwise.
 The dilation and thinning process~\cite{} is operated to remove small regions such as lanes and road overpasses and simplify the map.

\textbf{Data set linking.} The common ground of the two datasets is that they both have specific coordinates, which could be corresponding to the rasterized grid exactly.
For mobility data, we find the traffic flow of each region, and list the flow as vector by time.
And for POI data, we list the interests of POIs of each region as vector, and the dimension of this vector is equal to the quantity of POIs.
Now each region has two vectors, and they are the input of DMR.

\textbf{FRI on mobility data.} We use DMR~\cite{Yuan2012FunctionRegion} to identify region functionals and label them with 8 types. 
DMR is operate with hyper-parameters $\beta = 0.01$, variance $\sigma^2 = 1$
Note that we can use any convenient FRI system to identify region functionals.
The DMR results are illustrated in Figure~\ref{fig:DMR}

@@

\textbf{Text Cleaning.} 
A common used package for Chinese word segmentation is Jieba Segment Word.
We use it to deal with raw textual data and 
We gather 883 words with less information as stopwords.
To save memory and improve efficiency, the stopwords are removed from the segmented word list and don't continue the following analysis.
%activity extraction?  Sec3.1 has done.
Statistics of the combined dataset are shown in Table~\ref{tab:dataset}.
Averagely, a POI is associated with nearly 30 comments, a region is related to over 15000 mobility trajectories in 30 days,
 and a label contains over 100 regions.

\begin{table}[h]
\centering
\caption{Statistics of dataset}\label{tab:dataset}
\begin{tabular}{|c|c|c|c|c|}
\hline
\#POIs & \#Comments & \#Mobility pairs & \#Regions & \#Labels \\
\hline
109686 & 3213264 & 7065937 & 901 & 8 \\
\hline
\end{tabular}
\end{table}

\subsection{Urban Feature Extraction}
We aim to select suitable urban feature which has a strong distinction on various region functions.

\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) Frequency; (2)TF-IDF; (3)rule-based.

A simple baseline is to selected the nouns with highest frequency, i.e. appear in as much comments as possible.
The common approach to extract feature is term frequency¨Cinverse document frequency(TF-IDF) as:
$$TF-IDF(x) = TF(x)\times IDF(x) = (\log\frac{N}{N(x)})\times(\log\frac{N(x)}{N(x)+1}+1)$$
where $N$ is the quantity of whole text data ,and $N(x)$ is the quantity of text data contain word $x$
%Introduction of rule-based.I haven't find related tutorial

\textbf{Evaluation metrics.} These metrics are used to measure our performance:
(1)Normalization Discounted Cumulative Gain(NDCG); (2)p@n.

To evaluate the accuracy of urban feature extraction, five human volunteers are required to give every selected feature a rating $gain$ of ranges from 1 to 5.
NDCG is a common used measure, which incorporates graded relevance. The form is:
\begin{align*}
DCG_p&=\sum_{i=1}^{p}\frac{gain_i}{\log_2(i+1)}\\
DCG_p&=\sum_{i=1}^{|REL|}\frac{gain_i}{\log_2(i+1)}\\
NDCG_p&= \frac{DCG}{IDCG}
\end{align*}
NDCG@$k$ means that $k$ features are selected to be evaluated.
And p@n represents the proportion of features with cumulative Gain higher than 2 in n selected urban features.

\begin{table}[h]
\centering
\caption{Comparative performance of urban feature extraction}\label{tab:extraction}
\begin{tabular}{p{3.3cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}}
        \hline
        Extraction approach & p@5 & p@10 & p@15 & NDCG@3 & NDCG@5\\
        \hline
        Frequency &  &  &  & \\
        \hline
        TF-IDF &  &  &  & \\
        \hline
        rule-based &  &  &  & \\
        \hline
        EFRI &  &  &  & \\
        \hline
    \end{tabular}
\end{table}

As shown in Table~\ref{tab:extraction}, We can see that our EFRI model has a superior performance of urban feature extraction.

\subsection{Traffic Flow Prediction}

\textbf{Comparative Methods.} The prediction of EFRI is operated with layered regression.
There is some other approaches can estimate the prediction. (1)collaborative filtering; (2)EFRI withour bias curve $\beta$; (3) EFRI with normal feature.

CF is widely used in recommendation system.Therefore, prediction is one of the most application of CF.
Meanwhile, we compare with the variant form of EFRI to validate its advantage.

\textbf{Evaluation metrics.}It is a typical regression process and common used evaluate matrix is: (1)Mean Squared Error(MSE), (2)Root Mean Squared Error(RMSE), (3)Mean Absolute Error(MAE) (4)R Squared($R^2$).

They are typical metrics to measure the accuracy of regression model, and their form as:
$$MSE = \frac{1}{m}(y_i-\hat{y}_i)^2$$
$$RMSE = \sqrt{\frac{1}{m}(y_i-\hat{y}_i)^2}$$
$$MAE = \frac{1}{m}|y_i-\hat{y}_i|$$
$$R^2 = 1-\frac{MSE(\hat{y} , y)}{Var(y)}$$
where $y$ is the real value and $\hat{y}$ is the predict value given by regression;
$Var(y)$ is the variance of $y$.

\begin{table}[h]
    \centering
    \caption{Comparative performance of traffic flow prediction}\label{tab:prediction}
    \begin{tabular}{p{3.3cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}}%{c|c|c|c|c|c}
        \hline
        Prediction Approach & MSE & RMSE & MAE & $R^2$ \\
        \hline
        CF &  &  &  & \\
        \hline
        EFRI without $\beta$ &  &  &  & \\
        \hline
        EFRI with normal feature &  &  &  & \\
        \hline
        EFRI &  &  &  & \\
        \hline
    \end{tabular}
\end{table}
From Table~\ref{tab:prediction}, we confirm our confidence that EFRI has a more accurate result than other approaches in most metrics.
It turn out that EFRI could capture the interesting information in mobility patterns.
EFRI perform better than the same framework with normal feature, which also proves the accuracy of our urban feature extraction.

Besides, the variable $y_i$ corresponding to $x_i$ have been learn by EFRI, and we get parameter of $\beta(x)$.
The form of $\beta(x)$ with trained $y_i$ is shown in Figure~\ref{fig:beta}
\begin{figure}[h]
  \centering
  \label{fig:beta}
  \caption{The form of $\beta$ with a=1, t=weekend}
\end{figure}

@@

\textbf{Comparative Methods.} We compare EFRI with the following systems. (1)text-based explanation; (2)trajectory-based explanation.

EFRI based on the mixture application of mobility data and textual data.
We set the explanation given by a single data source as baseline to discuss the result of the heterogeneous data.

\textbf{Evaluation metrics.} Evaluation of explainable systems is still an open problem. In this work, we consider two categories of evaluation metrics. The first is objective to evaluate the quantity of explanations. (1)explainability precision(EP); (2)Explain quality.

To measure the explainability of these models, ~\cite{Abdollahi2017MEPMER} adopted MAP and MAR as evaluation metrics.
EP is percentage of regions that could find explanation label by our framework, which is defined as:
$$explanation\ percentage=\frac{|regions\ with\ explanation\ label|}{|all\ regions|}$$
And the rest are subjective to evaluate the quality of explanations.

All reported results are averaged over regions.

\textbf{Evaluation Process}
To measure the quality of explainability, five human volunteers are required to give every urban feature as explanation a rating.
The accurate labels get 5 stars while the incorrect get 1 star.
Our evaluation based on the average of the rating over humans.

\begin{table}[h]
\centering
\caption{Comparative performance of explainability }\label{tab:explainablity}
\begin{tabular}{p{3.3cm}|p{2.2cm}|p{2.2cm}|p{2.2cm}|p{2.2cm}}
        \hline
        Method & EP & Explain quality\\
        \hline
        text-based &  & \\
        \hline
        Trajectory-besed &  & \\
        \hline
        EFRI &  & \\
        \hline
    \end{tabular}
\end{table}

As shown in Table~\ref{tab:explainablity}, EFRI is outperformed than the baselines with single data source in both EP and quality.
It demonstrates that our mixture of the heterogeneous data improve the interpretability of FRI results.

@@

\bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
\bibitem{Zhang2014ExplicitFactor}Zhang Y, Lai G, Zhang M, et al. Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval. ACM, 2014:83-92.

\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017
\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63-72.
    %explain AI
\bibitem{Korpan2017navigation}Korpan, R., Epstein, S.L., Aroor, A., Dekel, G.: WHY: Natural explanations from a robot navigator. In: AAAI 2017 Fall Symposium on Natural Communication for Human-Robot Collaboration.
\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems. In Proceedings of the First International Workshop on Comprehensibility and Explanation in AI \& ML, 2017.
\bibitem{Lu2011Label}Lu Y, Castellanos M, Dayal U, et al. Automatic construction of a context-aware sentiment lexicon:an optimization approach[C]// International Conference on World Wide Web, WWW 2011, Hyderabad, India, March 28 - April. DBLP, 2011:347-356.
\bibitem{Zhang2017Model}Zhang X , Zhao J , Lui J C S . Modeling the Assimilation-Contrast Effects in Online Product Rating Systems: Debiasing and Recommendations[C]// Eleventh Acm Conference on Recommender Systems. ACM, 2017.
\bibitem{Mimno2012DMR}Mimno D, Mccallum A. Topic Models Conditioned on Arbitrary Features with Dirichlet-multinomial Regression[J]. University of Massachusetts - Amherst, 2012, 2008:411--418.
\bibitem{Mikolov2013Word2vec}Mikolov T , Sutskever I , Chen K , et al. Distributed Representations of Words and Phrases and their Compositionality[J]. Advances in Neural Information Processing Systems, 2013, 26:3111-3119.
\bibitem{Abdollahi2017MEPMER}Behnoush Abdollahi and Olfa Nasraoui. Using explainability for constrained matrix factorization. In Proceedings of the Eleventh ACM Conference on Recommender Systems, pages 79¨C83. ACM, 2017.
\end{thebibliography}
\end{document}
